---
title: "shRNA design to target circRNAs"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{shRNA design to target circRNAs}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
#install library
devtools::install_github("ipatop/circRNAshRNAdesign")
library(circRNAshRNAdesign)
```

# Description

This package contains ONE function that will generate a DataFrame or tab separated file with the original table with the shRNA oligo design appended. 

The input should be a tab sepparated table with circRNA back-splicing junction coordinates and gene names in the format: 

Name Chr Start End

This table can have an optional column with the Strand

So far the following species are available: 
fly: dm3, dm6 
human: hs19, and hg38
mice: mm10 
rat: rn4

# Requiered packages

The following packages are required, here how to install it

```
install.packages("dplyr")
install.packages("tidyr")
BiocManager::install("Rsubread")
BiocManager::install("GenomicFeatures")
BiocManager::install("Biostrings")
BiocManager::install("TxDb.Dmelanogaster.UCSC.dm6.ensGene")
BiocManager::install("BSgenome.Dmelanogaster.UCSC.dm6")
BiocManager::install("TxDb.Dmelanogaster.UCSC.dm3.ensGene")
BiocManager::install("BSgenome.Dmelanogaster.UCSC.dm3")
BiocManager::install("TxDb.Hsapiens.UCSC.hg19.knownGene")
BiocManager::install("BSgenome.Hsapiens.UCSC.hg19")
BiocManager::install("TxDb.Hsapiens.UCSC.hg38.knownGene")
BiocManager::install("BSgenome.Hsapiens.UCSC.hg38")
BiocManager::install("TxDb.Mmusculus.UCSC.mm10.knownGene")
BiocManager::install("BSgenome.Mmusculus.UCSC.mm10")
BiocManager::install("TxDb.Rnorvegicus.UCSC.rn4.ensGene")
BiocManager::install("BSgenome.Rnorvegicus.UCSC.rn4")
```

# Run example

Input should look like this
```{r}
head(read.delim("../test/circs_totest.txt"))
```

Run to create an output table
```{r}
OligoDesigner(input_coordinates = "../test/circs_totest.txt",output = "../test/New_out.tsv")
```

Run to create a DataFrame, if writetab = F
```{r}
oligos<-OligoDesigner(input_coordinates = "../test/circs_totest.txt",output = "../test/New_out.tsv",writetab = F)
```

Output
```{r}
head(oligos)
```


